### 2018-11-15 Sections/cloud_quantum_computing.tex
Fixed distributed search and added fig

\subsubsection{Quantum MapReduce}\index{Quantum MapReduce}

@@

>>>>

% Quantum MapReduce

\subsubsection{Quantum MapReduce}\index{Quantum MapReduce}\label{sec:quant_map_reduce}

@@

% Distributed quantum search algorithm

\subsubsection{Distributed quantum search algorithm}\index{Distributed quantum search algorithm}

The Grover quantum search algorithm (Sec.~\ref{sec:quantum_search}) can be easily parallelised\index{Parallelisation} by partitioning the search space\index{Search space!Partitioning}, and allocating a different partition to each node.

Suppose we wish to search over the $N$-bit space $x$, to find a satisfying solution to some oracle\index{Oracles} function (e.g when solving an \textbf{NP}-complete problem\index{NP \& NP-complete}),
\begin{align}
x\,\, \mathrm{s.t.}\, f(x)=1.
\end{align}
Let there be $M$ nodes available for computation, where for simplicity we assume $M$ is a power of 2 (although the idea works generally for arbitrary $M$, albeit not as mathematically elegantly). We designate each of the nodes a $\log_2 M$-bit identification number\index{Identification numbers},
\begin{align}
	y=[0,M-1].
\end{align}
We now program each node to search over a smaller search space $x'$, which is \mbox{$N-\log_2 M$} bits in length, concatenated with the node's identification number to produce the full range of $x$. The input to each instance of the oracle is now,
\begin{align}
x = x'\frown y,
\end{align}
where `$\frown$' denotes binary string concatenation.

For example, with four nodes the 2-bit identification numbers are, 
\begin{align}
	y=\{00,01,10,11\}.
\end{align}
If the input search space is $N$-bits in length, then each of the nodes are assigned the search-space \mbox{$x'\frown y$}, where $x'$ is an \mbox{$N-2$}-bit number. Within each instance, the Grover search searches over only the reduced space $x'$, with $y$ a constant of the instance. Fig.~\ref{fig:distributed_search} illustrates the circuit schematic for this simple example.

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{distributed_search}
	\caption{Example of a quantum \textsc{MapReduce} protocol for implementing a distributed quantum search over four nodes. Each node performs a quantum search over the reduced space $x'$, concatenated with the identification number of the node, which recovers the full search-space $x$ across all the nodes collectively. This effectively partitions and allocates the search-space across the nodes, which implement their reduced searches in parallel. The net speedup provided by $M$ nodes operating in parallel scales as $O(\sqrt{M})$.}\label{fig:distributed_search}\index{Distributed quantum search algorithm}
\end{figure}

It can easily be seen that this approach is compatible with the general quantum \textsc{MapReduce} formalism (Sec.~\ref{sec:quant_map_reduce}), where the \textsc{Map} function assigns the partitions denoted by the node identification numbers $y$, the \textsc{Execute} functions implement the reduced searches associated with each instance, and the \textsc{Reduce} function collects satisfying arguments from the instances,
\begin{align}
	x'\,\, \mathrm{s.t.}\, f(x'\frown y)=1\,\,\forall\, y.
\end{align}

From the runtime of the Grover algorithm, it follows that the time required to solve the search problem on the initial full search-space is $O(\sqrt{2^N})$, whereas the time required in the parallelised implementation is only $O(\sqrt{2^{N-\log_2 M}})$. Thus, the need speedup is,
\begin{align}
	O\left(\frac{\sqrt{2^N}}{\sqrt{2^{N-\log_2 M}}}\right) = O(\sqrt{M}).
\end{align}

Evidently, the net computational speedup scales as a factor of the square root of the number of nodes in the parallelised implementation. Note that this approach does not exploit entanglement between nodes, and does not offer a `quantum' (i.e super-polynomial) speedup, since it's really just brute-force partitioning of a problem into smaller, quicker, bite-sized chunks that are attacked completely independently of one another, much like classical parallelisation.

To the contrary, unlike most quantum algorithms, whose power grows exponentially with the number of qubits (increasing returns\index{Increasing returns}), the distributed quantum search algorithm exhibits diminishing returns\index{Diminishing returns} with the degree of parallelisation -- the computational gain from adding one additional node to the network scales as,
\begin{align}
O\left(\sqrt{\frac{M+1}{M}}\right) &= O\left(\sqrt{1+\frac{1}{M}}\right),\nonumber\\
\lim_{M\to\infty} O\left(\sqrt{1+\frac{1}{M}}\right) &= O(1).
\end{align}
That is, increasing the number of nodes from 1 to 2 has far greater net gain than increasing them from 100 to 101. In fact, asymptotically, the gain from adding an additional node vanishes in the limit of a high degree of parallelisation.

% Distributed unitary error averaging
